### 2023-11-07 cv/cv-body.tex
Add paper + doi
Add cjfas paper

@@

Conservation Biology. Preprint:
\url{https://doi.org/10.31235/osf.io/wgbpv}.
J. Nephin, P.L. Thompson, \textbf{S.C. Anderson}, A.E. Park, C.N.
Rooper, B. Aulthouse, J. Watson. Integrating disparate survey data in
species distribution models demonstrates the need for robust model
evaluation. In press at Canadian Journal of Fisheries and Aquatic
Science.

>>>>

Nephin, J., P.L. Thompson, \textbf{S.C. Anderson}, A.E. Park, C.N.
Rooper, B. Aulthouse, and J. Watson. Integrating disparate survey data
in species distribution models demonstrate the need for robust model
evaluation. In press at Can. J. Fish. Aquat. Sci.
\url{https://doi.org/10.1139/cjfas-2022-0279}.
Baker, K.D., \textbf{S.C. Anderson}, D.R.J. Mullowney, W. Walkusz, and
K.R. Skanes. Moving away from a scale mismatch: Spatiotemporal modelling
of striped shrimp (\emph{Pandalus montagui}) density in Canada's
subarctic. Fisheries Research. 270: 106898.
\url{https://doi.org/10.1016/j.fishres.2023.106898}.

@@

Conservation Biology. \url{https://doi.org/10.1111/cobi.14184}.
